\begin{thebibliography}{9}

\bibitem{boot1}
	Artwork blue skies boats paintings paper boat wallpaper. Opgehaald 31 Mei, 2016 van \url{http://www.allwallpaper.in/artwork-blue-skies-boats-paintings-paper-boat-wallpaper-4119.html}
	
	
\bibitem{wereldwijdeHandel}
	International Maritime Organisation. (n.d.). \emph{IMO profile}. Opgehaald 31 Mei, 2016 van \url{https://business.un.org/en/entities/13}

\bibitem{efficientstTransport}
	World Shipping Council. (n.d.). \emph{Efficiency}. Opgehaald 31 Mei, 2016 van \url{http://www.worldshipping.org/benefits-of-liner-shipping/efficiency}

\bibitem{hamiltonian}
	Ross, I. M. (2009). A Primer on Pontryagin's Principle in Optimal Control. \emph{Collegiate Publishers}.

\bibitem{een speedboot}
	SunCatcher. (n.d.). \emph{2015 V322 RF \(|\) V22 RF}. Opgehaald 23 Mei, 2016 van \url{http://www.suncatcherpontoons.com/v322-rf-v22-rf-pontoon}

\bibitem{Nijlbreedte}
	Wikipedia, the free encyclopedia. (2012). \emph{Nile}. Opgehaald 5 Juni, 2016 van \url{https://en.wikipedia.org/wiki/Nile}
	
\bibitem{bootstats}
	Harmer, J.  (2014). \emph{Average Pontoon Boat Speeds (With 15 Examples)} Opgehaald 23 Mei, 2016 van \url{http://pontoonguide.com/how-fast-pontoon-boat-speeds/}
	
\bibitem{Waterverplaatsing}
	Turnipseed, D.P., and Sauer, V.B., 2010, Discharge measurements at gaging 		stations: U.S. Geological Survey 
	Techniques and Methods book 3, chap. A8, 87 p2. (Also available at 
	\url{http://pubs.usgs.gov/tm/tm3-a8/}.)
	\begin{comment}	
	Turnipseed, D.P. en Sauer V.B. (2010). Discharge Measurements at Gaging Stations Chapter 8 of Book 3, Section A. \emph{Discharge Measurements at Gaging Stations: Velocity-Area Method}. U.S. Geological Survey, Reston, Virginia. (p.2).
	\end{comment}
	
\bibitem{Nijlstats}
	Shahin, M. (1985). \emph{Hydrology of The Nile Basin} Development of Water Science Chapter 21. International Institute for Hydraulic and Environmental Engineering Delft, The Netherlands. Elsevier Sience Publisher B.V. (p.48).
\end{thebibliography}
