\section{Discussion}
\subsection{Average number of generations with and without type switching}\label{subsec:discaveseg}
As mentioned in the conclusion, we could not find a proper fit for the distribution of $Y_{j}$ and $Y_{j,s}$, since it does not follow any standard discrete distribution like poisson, binomial, geometric or any other standard distribution. We doubt that the distributions of $Y_j$ or $Y_{j,s}$ are ever recorded in the literature. But in our opinion, the histograms (Figure \ref{fig:histogram}) provide a good approximation for the distributions. A remarkable observation was that the histograms, which can be defined as a random variable $h_n(x)=\frac{1}{n}\sum^n_{i=1}\mathbbm{1}_{a_{j-1}<x\leq a_j}$, for $x\in (a_{j-1},a_j]$ ($x$ a realisation of a random variable),  did not appear very random. What we mean here, is that when we plotted the histograms of several samples from the same $Y_j$, they were always nearly identical, which is not expected from a random variable. Although it was not confirmed by a statistical test, the observation points to a persumable very peculiar distribution of \(Y_j\).\\

Another remark about the histograms, is that unfortunately, there is a small convention error for the number of generations (an error which could not be corrected in time). Our model generation counters always started at 1 and thus by defnition, equilibrium can never be reached at the first generation. This convention is actually confusing because the counter would give 2 if 1 generation has passed. So in our model, we actually assumed that one generation has always passed. However, this error does not seem to affect the histogram more than just a shift of the mean.

\subsection{Average segregation time}
In line with section \ref{subsec:discaveseg}, a distribution of the $60\%$ and $80\%$ segregation times could not be found. We should note that, when running a simulation that takes 500 instances for a given happiness rule, some uncertaincy still remains. This is best shown in Figure \ref{fig:happyseg4b}, where, due to the discrete effect of the happiness rule, the average segregated fraction should be a perfect stairs pattern, but the figure shows some distortion. Of course, this is expected since 500 may be considered a 'large' number, but it still results in distortions. One could argue whether the step size for the happiness rule dependence should have been chosen larger. Since for second order neighbourhood, the number of possible happiness values is quite limited. However, due to the earlier mentioned inaccuracies, setting this step size too large decreases the accuracy of the figures that include happiness rule dependence.

\subsection{The effect of switching types}
As seen in Figure \ref{fig:avesegsw}, if conformity is allowed, the population will be nearly \(80\%\) homogenous after one generation. 
This gives rise to a critical note for this extension with respect to the standard board. It is our belief namely, that the standard board is too limited in size, number of types and population density. 
As a result the standard board will reach equilibrium in no more than 2 generations on average. On extremely rare occasions, it might take 7 generations to reach equilibrium (Figure  \ref{fig:histogramSw}). 

  